---
title: "Scraping and Analysis"
author: "Waleed Iftikhar and Sameer Swarup"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(tidyverse)
library(purrr)
library(survey)
library(forcats)
library(class)
library(readr)
library(tidyr)
library(randomForest)
library(caret)
library(partykit)
library(rpart)
```

*Scraping data from Wikipedia page on Ronaldo vs Messi rivalry*
```{r}
wikiurl <- "https://en.wikipedia.org/wiki/Ronaldo%E2%80%93Messi_rivalry#Club_statistics"
wikipage <- read_html(wikiurl)
```

*Extracting html table that has Messi and Ronaldo club club goals*
```{r}
#Extracting html table that has Messi and Ronaldo club goals
tables.html <- html_nodes(wikipage,"table")
clgls <- html_table(tables.html[[5]], fill = TRUE) %>% as_tibble()
```

*Creating a dataset of Messi Club Goals.*
```{r}
messiclgls <- clgls  %>%
  select(X1,X2,X3,X4,X5,X6,X7,X8,X9,X10,X11,X12)%>%
  slice(3:22) #Slicing tibble so that it has data on Messi from 2004 to 2020

messiclgls <- messiclgls %>%
  rename(Club = "X1", Season = "X2", LeagueApps = "X3", LeagueGoals = "X4", CupApps = "X5", CupGoals = "X6",EuropeApps = "X7", EuropeGoals = "X8",OtherApps = "X9", OtherGoals = "X10",TotalApps = "X11", TotalGoals = "X12" ) #Renaming columns

messiclgls <- messiclgls%>%
  slice(-(1:3))%>%
  slice(-17)
```

*Creating a dataset of Ronaldo Club Goals*
```{r}
crisclgls <- clgls  %>%
  select(X1,X2,X3,X4,X5,X6,X7,X8,X9,X10,X11,X12)%>%
  slice(23:47) #Slicing tibble so that it has club data on Ronaldo from 2002 to 2020

crisclgls <- crisclgls %>%
  rename(Club = "X1", Season = "X2", LeagueApps = "X3", LeagueGoals = "X4", CupApps = "X5", CupGoals = "X6",EuropeApps = "X7", EuropeGoals = "X8",OtherApps = "X9", OtherGoals = "X10",TotalApps = "X11", TotalGoals = "X12" ) #Renaming columns

crisclgls <- crisclgls%>%
  slice(-(1:3))%>%
  drop_na()
```

*Creating a dataset of international goals*
```{r}
intgls <- html_table(tables.html[[8]], fill = TRUE) %>% as_tibble()
```

*Creating a dataset of Messi International Goals.*
```{r}
messiintgls <- intgls  %>%
  select(X1,X2,X3,X4,X5,X6,X7,X8)%>%
  slice(3:19) #Slicing tibble so that it has data on Messi's stats for Argentina from 2005 to 2019

messiintgls <- messiintgls %>%
  rename(NationalTeam= "X1", Year = "X2", CompApps= "X3", CompGoals = "X4", FrndApps = "X5", FrndGoals = "X6",TotalApps = "X7", TotalGoals = "X8") #Renaming columns

messiintgls <- messiintgls%>%
  slice(-(1:2))
```

*Creating a dataset of Ronaldo International Goals.*
```{r}
crisintgls <- intgls  %>%
  select(X1,X2,X3,X4,X5,X6,X7,X8)%>%
  slice(23:41) ##Slicing tibble so that it has data on Ronaldo's stats for Portugal from 2003 to 2019

crisintgls <- crisintgls %>%
  rename(NationalTeam= "X1", Year = "X2", CompApps= "X3", CompGoals = "X4", FrndApps = "X5", FrndGoals = "X6",TotalApps = "X7", TotalGoals = "X8") #Renaming columns

crisintgls <- crisintgls%>%
  slice(-(1:2))
```

*Scraping data from MessivsRonaldo.net*
```{r}
urlCalendar <- "https://messivsronaldo.net/calendar-year-stats/"
pageCalendar <- read_html(urlCalendar)
```

*Getting all nodes of type unordered list (ul)*
```{r}
div.html <- html_nodes(pageCalendar, "ul")
```

*Getting all of messi's and ronaldo's stats from the ul parent nodes*
```{r}
messi <- html_nodes(pageCalendar, ".messi.stats")
ronaldo <- html_nodes(pageCalendar, ".ronaldo.stats")
```

*Making tibble out of messi stats*
```{r}
messiStats <- tibble(
  apps = messi %>% html_node(".apps") %>% html_text(),
  assists = messi %>% html_node(".assists") %>% html_text(),
  goals = messi %>% html_node(".goals .num") %>% html_text()
)
```

*Making tibble out of ronaldo stats*
```{r}
ronaldoStats <- tibble(
  apps = ronaldo %>% html_node(".apps") %>% html_text(),
  assists = ronaldo %>% html_node(".assists") %>% html_text(),
  goals = ronaldo %>% html_node(".goals .num") %>% html_text()
)
```

*Cleaning data from the messiStats dataframe*
```{r}
messiStatsparse <- messiStats %>%
  mutate(apps = parse_number(apps), assists = parse_number(assists), goals = parse_number(goals))%>%
  mutate(type = rep(c("Total", "Club", "Country"), nrow(messiStats)/3))
```

*Filtering Apps, Assists, and Goals based on Total, Club and Country*
```{r}
MTotals <- messiStatsparse%>%
  filter(type == "Total")
MClubs <- messiStatsparse%>%
  filter(type == "Club")
MCountries <- messiStatsparse%>%
  filter(type == "Country")
```

*Cleaning dataset to only contain total apps, goals and assists for Messi from 2002 to 2020.*
```{r}
MTotals <- MTotals %>%
  select(apps,assists,goals) %>%
  rename(MTotApps = "apps", MTotAssists = "assists", MTotGoals = "goals" )%>%
  mutate(Year = rep(2020:2002))%>%
  select(Year, MTotApps, MTotAssists, MTotGoals)
```

*Cleaning dataset to only contain club apps, goals and assists for Messi from 2002 to 2020.*
```{r}
MClubs <- MClubs %>%
  select(apps,assists,goals) %>%
  rename(MClubApps = "apps", MClubAssists = "assists", MClubGoals = "goals" )%>%
  mutate(Year = rep(2020:2002))%>%
  select(Year, MClubApps, MClubAssists, MClubGoals)
```

*Cleaning dataset to only contain international apps, goals and assists for Messi from 2002 to 2020.*
```{r}
MCountries <- MCountries %>%
  select(apps,assists,goals) %>%
  rename(MCoApps = "apps", MCoAssists = "assists", MCoGoals = "goals" )%>%
  mutate(Year = rep(2020:2002))%>%
  select(Year, MCoApps, MCoAssists, MCoGoals)
```

*Creating dataset and writing csv that has apps, goals and assists for Messi in club, country and total.*
```{r}
MessiPartial <- left_join(MTotals,MClubs, by = "Year")
MessiComplete <- left_join(MessiPartial, MCountries, by = "Year")
write_csv(MessiComplete, "MessiComplete.csv")
```

*Cleaning data from the ronaldoStats dataframe*
```{r}
ronaldoStatsparse <- ronaldoStats %>%
  mutate(apps = parse_number(apps), assists = parse_number(assists), goals = parse_number(goals))%>%
  mutate(type = rep(c("Total", "Club", "Country"), nrow(ronaldoStats)/3))
```

```{r}
RTotals <- ronaldoStatsparse%>%
  filter(type == "Total")
RClubs <- ronaldoStatsparse%>%
  filter(type == "Club")
RCountries <- ronaldoStatsparse%>%
  filter(type == "Country")
```

```{r}
RTotals <- RTotals %>%
  select(apps,assists,goals) %>%
  rename(RTotApps = "apps", RTotAssists = "assists", RTotGoals = "goals" )%>%
  mutate(Year = rep(2020:2002))%>%
  select(Year, RTotApps, RTotAssists, RTotGoals)
```

```{r}
RClubs <- RClubs %>%
  select(apps,assists,goals) %>%
  rename(RClubApps = "apps", RClubAssists = "assists", RClubGoals = "goals" )%>%
  mutate(Year = rep(2020:2002))%>%
  select(Year, RClubApps, RClubAssists, RClubGoals)
```

```{r}
RCountries <- RCountries %>%
  select(apps,assists,goals) %>%
  rename(RCoApps = "apps", RCoAssists = "assists", RCoGoals = "goals" )%>%
  mutate(Year = rep(2020:2002))%>%
  select(Year, RCoApps, RCoAssists, RCoGoals)
```

```{r}
RonaldoPartial <- left_join(RTotals,RClubs, by = "Year")
RonaldoComplete <- left_join(RonaldoPartial, RCountries, by = "Year")
write_csv(RonaldoComplete, "RonaldoComplete.csv")
```

*Joining the MessiComplete and RonaldoComplete Dataframes*
```{r}
StatsComplete <- inner_join(MessiComplete, RonaldoComplete, by = "Year")
```

*Datawrangling from Trophy_Comparison dataset*
```{r}
RonaldoTrophies <- Trophy_Comparison%>%
  filter(Player == "Ronaldo")
MessiTrophies <- Trophy_Comparison%>%
  filter(Player == "Messi")
```

```{r}
RonaldoTrophies1 <- RonaldoTrophies %>%
  select(Year, League, DomesticCup, EuropeanCup) %>%
  rename(RLeague = "League", RDomesticCup = "DomesticCup", REuropeanCup = "EuropeanCup")
MessiTrophies1 <- MessiTrophies %>%
  select(Year, League, DomesticCup, EuropeanCup) %>%
  rename(MLeague = "League", MDomesticCup = "DomesticCup", MEuropeanCup = "EuropeanCup")
```

```{r}
Trophies <- inner_join(MessiTrophies1, RonaldoTrophies1, by = "Year")
```

```{r}
WithoutAward <- inner_join(StatsComplete, Trophies, by = "Year")
```

```{r}
WithoutAwardFilter <- WithoutAward %>%
  filter(Year >= 2008 & Year != 2018)
```

```{r}
WithAward <- WithoutAwardFilter %>%
  mutate(BallonDor = c("Messi", "Ronaldo", "Ronaldo","Messi", "Ronaldo", "Ronaldo", "Messi", "Messi", "Messi", "Messi", "Ronaldo"))
write_csv(WithAward, "MessiRonaldoComplete.csv")
```


*Scraping data on Messi goals in competitions.*
```{r}
messiClubStatsURL <- "https://www.transfermarkt.us/lionel-messi/detaillierteleistungsdaten/spieler/28003"
```

```{r}
messiClubStatsPage <- read_html(messiClubStatsURL)
```

```{r}
messiTable.html <- html_nodes(messiClubStatsPage, "table")
```

```{r}
messiLaLiga <- html_table(messiTable.html[[1]], fill = TRUE) %>% as_tibble(.name_repair = "unique")

messiLaLiga <- messiLaLiga %>% select(Season, Club, ...6, ...7) %>% rename(Appearances = "Club", Goals = "...6", Assists = "...7") %>% drop_na() %>% slice(3:11)
messiLaLiga <- messiLaLiga %>%
  mutate(Player = "Messi")
```

*Scraping data on Ronaldo goals in competitions.*
```{r}
ronaldoClubStatsURL <- "https://www.transfermarkt.us/cristiano-ronaldo/detaillierteleistungsdaten/spieler/8198"
```

```{r}
ronaldoClubStatsPage <- read_html(ronaldoClubStatsURL)
```

```{r}
ronaldoTable.html <- html_nodes(ronaldoClubStatsPage, "table")
```

```{r}
ronaldoLaLiga <- html_table(ronaldoTable.html[[1]], fill = TRUE) %>% as_tibble(.name_repair = "unique")

ronaldoLaLiga <- ronaldoLaLiga %>% select(Season, Club, ...6, ...7) %>% rename(Appearances = "Club", Goals = "...6", Assists = "...7") %>% drop_na() %>% slice(3:11)
ronaldoLaLiga <- ronaldoLaLiga %>%
  mutate(Player = "Ronaldo")
```

*Join the Messi and Ronaldo datasets for each competition*
```{r}
#LaLiga
messiAndRonaldoLaLiga <- rbind(messiLaLiga, ronaldoLaLiga)%>%
  select(Season, Player, Appearances, Goals, Assists)
```

```{r}
write_csv(messiAndRonaldoLaLiga, "messiAndRonaldoLaLiga.csv")
```

```{r}
messiChampionsLeague <-  html_table(messiTable.html[[3]], fill = TRUE) %>% as_tibble(.name_repair = "unique")

messiChampionsLeague <- messiChampionsLeague %>% select(Season, Club,...6, ...7) %>% rename(Appearances = "Club", Goals = "...6", Assists = "...7") %>% drop_na() %>% slice(3:19)

messiChampionsLeague <- messiChampionsLeague %>% slice(-(c(4,5,10,11,14,15,17)))%>%
  mutate(Player = "Messi")
```

```{r}
ronaldoChampionsLeague <-  html_table(ronaldoTable.html[[3]], fill = TRUE) %>% as_tibble(.name_repair = "unique")

ronaldoChampionsLeague <- ronaldoChampionsLeague %>% select(Season, Club,...6, ...7) %>% rename(Appearances = "Club", Goals = "...6", Assists = "...7") %>% drop_na() %>% slice(3:19)

ronaldoChampionsLeague <- ronaldoChampionsLeague %>% slice(-(c(2,3,5,8,9,16,17)))%>%
  mutate(Player = "Ronaldo")
```

```{r}
#ChampionsLeague
messiAndRonaldoUEFA <- rbind(messiChampionsLeague, ronaldoChampionsLeague)%>%
  mutate(Assists = parse_number(Assists) )
```

```{r}
write_csv(messiAndRonaldoUEFA, "messiAndRonaldoUEFA.csv")
```

##Statistical Learning on the Dataset

###Fitting a Random Forests Model on the Dataset `MessiRonaldoComplete` 

###Converting all binary variables from character to factors. Taking out All the total stats because they are just the sum of the club and country stats.
```{r}
MessiRonaldoComplete1<- read.csv("MessiRonaldoComplete.csv") %>%
  select(-MTotAssists, -MTotGoals,- MTotApps, - RTotAssists, - RTotGoals, - RTotApps)
```

*Splitting the training data into a training subset and a test subset.*

```{r Training/Test Split}
set.seed(757302859)
n <- nrow(MessiRonaldoComplete1)
train_index <- sample(n, size=round(.8*n))
BDor_train <- MessiRonaldoComplete1 %>% slice(train_index)
BDor_test <- MessiRonaldoComplete1 %>% slice(-train_index)
```

###Tuning the value of mtry.

```{r Tuning Random Forest With All Variables}
set.seed(757302850)
train_control <- trainControl(
  method = "cv",   # cross-validation 
  number = 10     # 10-folds
)
randomforest_cv <- train(
  BallonDor ~ .,            # predict election winner using all other variables in training
  data = BDor_train,    # training data
  method = "rf",           # classification method
  tuneGrid = data.frame(mtry = seq(6,10, by = 1)),
  trControl = train_control    # validation method
)
randomforest_cv
```

```{r Random Forest With All Variables}
set.seed(2242021)
BallonDor_rforest <- randomForest(BallonDor ~ ., 
                                 data=BDor_train,
                                 ntree=200, 
                                 mtry = 10)
BallonDor_rforest
```

```{r Variable Importance Plot}
varImpPlot(BallonDor_rforest)
```

```{r RF Confirmation Matrix All Variables}
confm_test <- confusionMatrix(
  data = predict(BallonDor_rforest, newdata=BDor_test), 
  reference = BDor_test$BallonDor, 
  positive = "Messi" )
confm_test$table
confm_test$byClass
```

*Taking out the Domestic Cup Variable because it is not important in determining who wins Ballon D'or.*

###Tuning the value of mtry.

```{r Tuning Random Forest Without Domestic Cups}
set.seed(757302)
train_control <- trainControl(
  method = "cv",   # cross-validation 
  number = 10     # 10-folds
)
randomforest_cv1 <- train(
  BallonDor ~ MClubApps + MClubAssists + MClubGoals+ MCoApps  + MCoAssists +MCoGoals + MDomesticCup + MEuropeanCup + MLeague + RClubApps + RClubAssists + RClubGoals   + RCoApps + RCoAssists + RCoGoals + RDomesticCup+ REuropeanCup + RLeague+ Year,            # predict election winner using all other variables in training
  data = BDor_train,    # training data
  method = "rf",           # classification method
  tuneGrid = data.frame(mtry = seq(6,10, by = 1)),
  trControl = train_control    # validation method
)
randomforest_cv1
```

```{r Random Forest Without Domestic Cups}
set.seed(2242)
BallonDor_rforest1 <- randomForest(BallonDor ~ MClubApps + MClubAssists + MClubGoals+ MCoApps  + MCoAssists +MCoGoals + MDomesticCup + MEuropeanCup + MLeague + RClubApps + RClubAssists + RClubGoals   + RCoApps + RCoAssists + RCoGoals + RDomesticCup+ REuropeanCup + RLeague+ Year , 
                                 data=BDor_train,
                                 ntree=200, 
                                 mtry = 10)
BallonDor_rforest1
```

```{r Variable Importance Plot}
varImpPlot(BallonDor_rforest1)
```

```{r RF Confirmation Matrix without Domestic Cup}
confm_test <- confusionMatrix(
  data = predict(BallonDor_rforest, newdata=BDor_test), 
  reference = BDor_test$BallonDor, 
  positive = "Messi" )
confm_test$table
confm_test$byClass
```

*Trying a different type of statistical learning method*

###Logistic Regression

```{r}
BDor_logistic <- glm(BallonDor~ ., data=BDor_train, family = binomial)
```

```{r}
BDor_test2 <- BDor_test %>% 
  mutate(prob = predict(BDor_logistic , newdata = BDor_test, type = "response"),
         prediction = ifelse(prob > 0.5, "Messi", "Ronaldo"),
         prediction = fct_relevel(prediction, "Ronaldo", "Messi"))
```

###Determining the appropriate threshold level that maximizes accuracy. 
```{r}
t <- seq(0.05, 0.95, by = 0.05)
eval_fun <- function(t, test) 
  {test %>%
  mutate(prediction = ifelse( prob > t, "Messi", "Ronaldo") ) %>%
  summarize(threshold=t, 
            accuracy = mean(prediction == BallonDor), 
            sensitivity = sum(prediction == "Messi" & BallonDor == "Messi")/sum(BallonDor == "Messi"),
            specificity = sum(prediction == "Ronaldo" & BallonDor == "Ronaldo")/sum(BallonDor == "Ronaldo"),
            precision = sum(prediction == "Messi" & BallonDor == "Messi")/sum(prediction == "Messi"))
}
eval_df <- map_df(t, eval_fun, test = BDor_test2)
glimpse(eval_df)
```

All thresholds return the same value of accuracy, precision, sensitivity, and specificity. Moreover, the REuropean Cup variable seems to almost perfectly capture the behavior of Ballon D'or. Therefore, we will try to reduce the number of predictor variables we are using based on our background knowledge to a number which is lesser than the number of observations to see if that improves our model.

We deem that the number of appearances a player makes for either their club or country, the number of times they assist another player in scoring a goal and whether their team wins the Domestic Cup or not are not very important in determining whether they should win the Ballon D'or or not. Therefore, we will fit a logistic regression model without these predictor variables.

```{r}
BDor_logistic2 <- glm(BallonDor~ MClubGoals +MCoGoals + MEuropeanCup + MLeague+ RClubGoals + RCoGoals+ REuropeanCup + RLeague, data=BDor_train, family = binomial)
```

```{r}
BDor_test3 <- BDor_test %>% 
  mutate(prob = predict(BDor_logistic , newdata = BDor_test, type = "response"),
         prediction = ifelse(prob > 0.5, "Messi", "Ronaldo"),
         prediction = fct_relevel(prediction, "Ronaldo", "Messi"))
```

###Determining the appropriate threshold level that maximizes accuracy. 
```{r}
t <- seq(0.05, 0.95, by = 0.05)
eval_fun <- function(t, test) 
  {test %>%
  mutate(prediction = ifelse( prob > t, "Messi", "Ronaldo") ) %>%
  summarize(threshold=t, 
            accuracy = mean(prediction == BallonDor), 
            sensitivity = sum(prediction == "Messi" & BallonDor == "Messi")/sum(BallonDor == "Messi"),
            specificity = sum(prediction == "Ronaldo" & BallonDor == "Ronaldo")/sum(BallonDor == "Ronaldo"),
            precision = sum(prediction == "Messi" & BallonDor == "Messi")/sum(prediction == "Messi"))
}
eval_df <- map_df(t, eval_fun, test = BDor_test3)
glimpse(eval_df)
```

All thresholds still return the same value of accuracy, precision, sensitivity, and specificity. Moreover, the REuropean Cup variable still perfectly captures the behavior of Ballon D'or. However, we cannot remove this variable as the European Cup is the most important competition each year and if a player wins it they are almost guaranteed to win the Ballon D'or. For Cristiano Ronaldo, in particular, every year that he has been a part of the European Cup winning team, he has almost certainly won the Ballon D'or.
Therefore, our model has illustrated how important the European Cup is in determining the winner of the Ballon D'or. It has given us evidence that when predicting the winner of the Ballon D'or a certain year, it is very important to consider whether the player won the European Cup with their team. If they did, then it is very likely that they will in fact win the Ballon D'or.




